Illustrating Text

### 2015-12-10 paper/paper.tex
Some stylistic fixes to the paper as well as minor edits. Expanded image subsets to use the avg pixel comparator if used from the command line

\paragraph{}
Generating datasetss for related problems
Another application is generating datasets for other related problems such as trying to 
describe a given image. The task has been tried before and this could potentially generate
a dataset for training a neural network for doing the task. This probably could be best 
achieved by building a dataset for training an object recognition network. In the simplest
form of the problem we are setting out to achieve could result in providing a set of collages
with images keyed to a certain location in each matrix produced from a keyword/phrase set.

@@

\section{Related Work}
Related Work
-- Computer Vision

@@

\section{Generating Salient Keyword/Phrase Sets}
Generating salient sets is fairly easy compared with establishing a language model. To get a set of 
salient-words for a given article we provide the statistics for a given article and take the language 
model for the article. We use the language model to remove non-salient words from the article and then 
use some combination of statistics of the word for the article and in the language. It is hard to
determine a good combination of the statistics that represent the salience of a given word or word-set. 
Determining a statistic that represents good salience for a word or word-set is a problem on its own.
\paragraph{}
In this paper we choose a the combination:
$$1-frequencyInArticle(Word)/numberOfWordsInArticle$$
to represent the salience of a word or word-set.
\paragraph{}
We also use two thresholds to remove non-salient words. One is the percent of articles that a word or
word-set appears in and the other is how many occurences does the word appear overall.

\section{Generating Image Sets}
In our project we require a large number of images with similar annotations of keywords for each language 
used. The keywords for certain images may differ for each image, but there should be an intersection among 
the images for a select set of keywords. Since this is difficult to obtain on our own we, in our project, 
turned to google to obtain sets of images for keywords.
\paragraph{}
In generating a number of seperate sets for each set of salient keyword/phrase sets, we hope to be able
to determine whether there are any sets, generated by different texts, that are similar enough to be
considered the same. If they are similar enough it follows that the texts are encoding the same material 
and we can possibly say that if the articles are in different languages then they are approximate 
translations of each other.
\paragraph{}
After downloading images from the Google search image API of salient word sets from the article, the common 
subset of images within these sets must be found. This can be done by finding the intersection of all the 
sets. In our implemnetation, we first created subset that was the intersection of two sets and then 
iteratively performed the intersection of this subset with each other set of images. Since the number of 
images is relatively large, all the images in two sets could not be loaded into memory at once. To deal with 
this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images 
into memory, then compares each image in 1 block to each image in the other block and output images which are 
in both blocks. To compare the images two different comparison tests were used. For two images to be considered 
the same, they must pass either or both of the comparison tests. The first test was a simple pixel by pixel 
comparison, if for each pixel in each image the values of the pixels were equal then the two images are the 
same. The second comparison test was to take the average colour of all the pixels in a different square regions 
of the images and compare them. If the average colours in each of the regions were the same, then the images 
are considered the same.

\section{Generating Illustrations}
The last and final step in our project is how we visualize the image-sets and the keyword salience. Ideally we 
would be able to combine the images into a single images, but that is a difficult task even if we know what 
features and feature-groups a keyword or keyword-set relates to. Instead we opted for creating collage of the 
images within a set. This means that we would generate something similar to what one might expect an output of 
a model for object segmentation. There are no masks of objects, but we might expect that certain positions in 
a matrix to be occupied by a certain object for a salient set.
\paragraph{}
In arranging images in a collage we get around the problem of trying to combine them and possibly provide 
something in way of a story arc. It should show more meaningful visualization of the article at the origin of 
the matrix then in other places, provided that the salience measure is correct. It is also fairly culturally 
ambiguous since a lot of cultures have come to expect items to start in the top-left in recent times. But, 
there are more culturally ambiguous ways to create illustrations as well (which are more difficult).

\section{Conclusion and Problems}
One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so 
gathering enough images for each of the salient sets was impossible. This in turn has made it impossible to 
get the results we would consider significant. To obtain the results we want we will need access to a database 
that we can obtain a much larger set of images for each salient set. This may be achieved by data-mining for
images based on the salient sets themselves. Though there are possible ways of reducing the requirement of a
large amount of images which are discussed later.
\paragraph{}
Another problem is validation of results. Since we were unable to obtain the results needed, it is not relevant
that we cannot evaluate them. But, it needs to be discussed how we would go about evaluating the results had 
we obtained them. For this task we probably we need to crowd-source in order to have people evaluate the accuracy 
of the results. It isn't out of ordinary to need actual people to be involved the actual evaluation of the results. 
In computer vision a lot of data for evaluating models for generating salience or object segmentation have manually 
generated data from people. For us, we would not need any special tools such as eye-tracking tools to determine 
the accuracy though.

@@

\subsection{Language Model}
A possible extension of how we generate a language model is to take into account the time each article is written and 
published. We expect that certain words are more likely to be published during certain time periods of the year such as 
during holidays (e.g. Christmas, Thanksgiving). Also, articles related to a crisis would likely be published during a 
certain span of time and possibly articles would be published in rememberance of them (e.g. 911).
\paragraph{}
In many languages their is a tendency for certain word-parts to take a certain order which may vary for a number of 
reasons such as whether a phrase is a question or statement. In later iterations of our language model we can take 
this into account and try to determine whether a language has such an order and when or whether it changes during 
certain contexts. We can determine whether there is a word order by determining if two or more words appear 
along-side each other relatively frequently.
\paragraph{}
Another concern about word-parts is that certain parts, such as nouns, may be considered more salient for illustration. 
It may be possible to determine whether a particular word is a noun, verb, etc. \ by considering their frequency 
along-side closely occuring words and their order. But, this is a difficult task on its own.
\paragraph{}
Another consideration is that some languages compound words together or have prefixes and suffixes attached to words in certain contexts. 
In order for us to determine whether a word occurs within a compound word would be to check whether it appears alone, 
it's frequency overall (the word `a' is likely to appear in a lot of words, but it is not a subword), and its frequency as a subword.
\paragraph{}
The task of getting relevant salient sets of words isn't necessarily resrticed to apriori methods or even traditional 
data-mining techniques. In a way using non-apriori methods may detract from ascertaining the meaning from the image sets 
we find. But, their results could still be considered interesting and relevant. It would be an interesting task to design 
a neural network to determine word salience or even to get it to create the illustrations. Some machine learning and a 
training set to determine thresholds for what is and is not salient could go a long ways. The thresholds would probably 
maintain relevance across different methods of solving the problem, but right now we are only guessing and manually 
adjusting them.

\subsection{Image Analysis and Partitioning of Image Sets}
A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find 
features and feature-groups within an image. Using features and feature-groups we may be able to find which features 
or feature-groups relate to each keyword or keyword-set and pick images based on this. This step is already improved 
if we are able to match multiple modifications of a single image and throwing away the modified versions. Looking at 
an image on a feature basis allows us to generate a better set of images that represent the keywords better and means 
that we possibly won't need to have as large of a database of images with similar keyword/phrase annotations.
\paragraph{}
Learning to relate features and feature-groups to keywords and keyphrases can be done independently for each language. 
It may be possible to completely get around a need for a single database of images with keyword/phrase annotations 
for all languages. This would be the best modification to our project and product the best results. One of the biggest 
problems is the database for the images.

\subsection{Illustration}
The step of creating the illustration can be modified in a number of ways. The best method likely varies based on what 
you want to use the results for. For language learning and depending on the text size, it is probably best to either 
find a single image that is representitive of the salient set it represents or to be able to combine the images or 
features related to the keywords into an image. In some cases it probably would be best to have a series of images 
to represent a meaning. Illustrating certain actions would probably require multiple images to be accuratley 
illustrated.
\end{document}

>>>>

\paragraph{}
Generating datasets for related problems.
Another application is generating datasets for other related problems such as trying to 
describe a given image. The task has been tried before and this could potentially generate
a dataset for training a neural network for doing the task. This probably could be best 
achieved by building a dataset for training an object recognition network. In the simplest
form of the problem we are setting out to achieve could result in providing a set of collages
with images keyed to a certain location in each matrix produced from a keyword/phrase set.

@@

\section{Related Work}
Related Work
-- Computer Vision, Natural Language Processing

@@

\section{Generating Salient Keyword/Phrase Sets}

\paragraph{}
Generating salient sets is fairly easy compared with establishing a language model. To get a set of 
salient-words for a given article we provide the statistics for a given article and take the language 
model for the article. We use the language model to remove non-salient words from the article and then 
use some combination of statistics of the word for the article and in the language. It is hard to
determine a good combination of the statistics that represent the salience of a given word or word-set. 
Determining a statistic that represents good salience for a word or word-set is a problem on its own.
\paragraph{}
In this project we choose a the combination:
$$1-frequencyInArticle(Word)/numberOfWordsInArticle$$
to represent the salience of a word or word-set.
\paragraph{}
We also use two thresholds to remove non-salient words. One is the percent of articles that a word or
word-set appears in and the other is how many occurences does the word appear overall.

\section{Generating Image Sets}

\paragraph{}
In our project we require a large number of images with similar annotations of keywords for each language 
used. The keywords for certain images may differ for each image, but there should be an intersection among 
the images for a select set of keywords. Since this is difficult to obtain on our own we, in our project, 
turned to google to obtain sets of images for keywords.
\paragraph{}
In generating a number of seperate sets for each set of salient keyword/phrase sets, we hope to be able
to determine whether there are any sets, generated by different texts, that are similar enough to be
considered the same. If they are similar enough it follows that the texts are encoding the same material 
and we can possibly say that if the articles are in different languages then they are approximate 
translations of each other.
\paragraph{}
After downloading images from the Google search image API of salient word sets from the article, the common 
subset of images within these sets must be found. This can be done by finding the intersection of all the 
sets. In our implementation, we first created subset that was the intersection of two sets and then 
iteratively performed the intersection of this subset with each other set of images. Since the number of 
images is relatively large, all the images in two sets could not be loaded into memory at once. To deal with 
this issue, the intersection algorithm used was a block-based intersection which loads two blocks of 50 images 
into memory, then compares each image in 1 block to each image in the other block and output images which are 
in both blocks. To compare the images two different comparison tests were used. For two images to be considered 
the same, they must pass either or both of the comparison tests. The first test was a simple pixel by pixel 
comparison, if for each pixel in each image the values of the pixels were equal then the two images are the 
same. The second comparison test was to take the average colour of all the pixels in a different square regions 
of the images and compare them. If the average colours in each of the regions were the same, then the images 
are considered the same.

\section{Generating Illustrations}
\paragraph{}
The last and final step in our project is how we visualize the image-sets and the keyword salience. Ideally we 
would be able to combine the images into a single images, but that is a difficult task even if we know what 
features and feature-groups a keyword or keyword-set relates to. Instead we opted for creating collage of the 
images within a set. This means that we would generate something similar to what one might expect an output of 
a model for object segmentation. There are no masks of objects, but we might expect that certain positions in 
a matrix to be occupied by a certain object for a salient set.
\paragraph{}
In arranging images in a collage we get around the problem of trying to combine them and possibly provide 
something in way of a story arc. It should show more meaningful visualization of the article at the origin of 
the matrix then in other places, provided that the salience measure is correct. It is also fairly culturally 
ambiguous since a lot of cultures have come to expect items to start in the top-left in recent times. But, 
there are more culturally ambiguous ways to create illustrations as well (which are more difficult).

\section{Conclusion and Problems}
\paragraph{}
One problem we encountered was that the Google image seach API only allows for 100 searches per day for free, so 
gathering enough images for each of the salient sets was impossible. This in turn has made it impossible to 
get the results we would consider significant. To obtain the results we want we will need access to a database 
that we can obtain a much larger set of images for each salient set. This may be achieved by data-mining for
images based on the salient sets themselves. Though there are possible ways of reducing the requirement of a
large amount of images which are discussed later.
\paragraph{}
Another problem is validation of results. Since we were unable to obtain the results needed, it is not relevant
that we cannot evaluate them. But, it needs to be discussed how we would go about evaluating the results had 
we obtained them. For this task we probably we need to crowd-source in order to have people evaluate the accuracy 
of the results. It isn't out of ordinary to need actual people to be involved the actual evaluation of the results. 
In computer vision a lot of data for evaluating models for generating salience or object segmentation have manually 
generated data from people. For us, we would not need any special tools such as eye-tracking tools to determine 
the accuracy though.

@@

\subsection{Language Model}
\paragraph{}
A possible extension of how we generate a language model is to take into account the time each article is written and 
published. We expect that certain words are more likely to be published during certain time periods of the year such as 
during holidays (e.g. Christmas, Thanksgiving). Also, articles related to a crisis would likely be published during a 
certain span of time and possibly articles would be published in rememberance of them (e.g. 911).
\paragraph{}
In many languages their is a tendency for certain word-parts to take a certain order which may vary for a number of 
reasons such as whether a phrase is a question or statement. In later iterations of our language model, we would take 
this into account and try to determine whether a language has such an order and when or whether it changes during 
certain contexts. We can determine whether there is a word order by determining if two or more words appear 
along-side each other relatively frequently.
\paragraph{}
Another concern about word-parts is that certain parts, such as nouns, may be considered more salient for illustration. 
It may be possible to determine whether a particular word is a noun, verb, etc. \ by considering their frequency 
along-side closely occuring words and their order. However, this is a difficult task on its own.
\paragraph{}
Another consideration is that some languages compound words together or have prefixes and suffixes attached to words in certain contexts. 
In order for us to determine whether a word occurs within a compound word would be to check whether it appears alone, 
it's frequency overall (the word `a' is likely to appear in a lot of words, but it is not a subword), and its frequency as a subword.
\paragraph{}
The task of getting relevant salient sets of words isn't necessarily resrticed to apriori methods or even traditional 
data-mining techniques. In a way using non-apriori methods may detract from ascertaining the meaning from the image sets 
we find. But, their results could still be considered interesting and relevant. It would be an interesting task to design 
a neural network to determine word salience or even to get it to create the illustrations. Some machine learning and a 
training set to determine thresholds for what is and is not salient could go a long ways. The thresholds would probably 
maintain relevance across different methods of solving the problem, but right now we are only guessing and manually 
adjusting them.

\subsection{Image Analysis and Partitioning of Image Sets}
\paragraph{}
A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find 
features and feature-groups within an image. By using features and feature-groups, we may be able to find which features 
or feature-groups relate to each keyword or keyword-set and pick images based on this. This step is already improved 
if we are able to match multiple modifications of a single image and throwing away the modified versions. Looking at 
an image on a feature basis allows us to generate a better set of images that represent the keywords better and means 
that we possibly won't need to have as large of a database of images with similar keyword/phrase annotations.
\paragraph{}
Learning to relate features and feature-groups to keywords and keyphrases can be done independently for each language. 
It may be possible to completely get around a need for a single database of images with keyword/phrase annotations 
for all languages. This would be the best modification to our project and product the best results. One of the biggest 
problems is the database for the images.

\subsection{Illustration}
\paragraph{}
The step of creating the illustration can be modified in a number of ways. The best method likely varies based on what 
you want to use the results for. For language learning and depending on the text size, it is probably best to either 
find a single image that is representitive of the salient set it represents or to be able to combine the images or 
features related to the keywords into an image. In some cases it probably would be best to have a series of images 
to represent a meaning. Illustrating certain actions would probably require multiple images to be accuratley 
illustrated.
\end{document}
